Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-03 paper/ms.tex
update ms

\newcommand{\rprs}{{$R_p/R_{\star}$}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}

\newcommand{\teff}{T_{\rm eff}}
\newcommand{\ms}{M_\star}
\newcommand{\rs}{R_\star}

\newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}

@@

\newcommand{\eg}{e.g.,}

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae \citep{2021isma.book.....B},
occultations by gas-rich circumstellar disks
\citep{2017MNRAS.470..202B}, and, in geometrically favorable
circumstances, eclipses by stars and planets
\citep{2010exop.book...55W}.  More exotic forms of optical variability
relevant to this work include transiting exocomets (e.g. $\beta$~Pic;
\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
both M-dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).

@@

A word on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  The
CQVs should not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses whose optical variability is linked
to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  At the risk of
introducing yet another standard, we prefer a nomenclature that
reflects how, when observed over timescales of more than tens of
cycles, CQVs are almost but not exactly periodic.  They are
irregularly periodic, or for short, quasiperiodic.  While the
three-type classification scheme proposed by
\citet{2017AJ....153..152S} may indeed provide some helpful visual
distinctions amongst CQV sub-classes, it seems likely that they are
all explained by a single underlying phenomenon, and so we opt to
refer to them by a single empirically descriptive name.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  In order left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Plausible cartoon models for the phenomenon.  The
		dust clump scenario seems most plausible, given
    the stability of the dips, their chromaticity, the lack of
    observed infrared excesses, and the challenge of producing
    broadband opacity variations with only ionized hydrogen in the
    prominence scenario.
	}
	\label{fig:f1}
\end{figure*}

@@

We visually assessed whether the objects found using the Fourier
(Section~\ref{subsec:fourier}) and dip-counting
(Section~\ref{subsec:counting}) techniques were consistent with
expectations for CQVs by assembling the data shown in
Appendix~\ref{app:vetting}.  We labeled a star as a ``good'' CQV if
at least one TESS sector showed what we viewed as the unambiguous
signatures of the class (short period; at least three dips or else
otherwise oddly-shaped dips; relative stability over a timescale of
30\,days).  We also noted stars that we thought could be CQVs, but
that were more ambiguous with a ``maybe'' flag.

@@

The two ``good'' IR excesses belonged to ``candidate'' CQVs
TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
Hydrae association ($\approx$10\,Myr), and have relatively long
periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
we labeled both as ``maybe'' CQVs because the dips in their light
curves did not show the rigid periodicity typical of CQVs;  their
periods were also relatively long.  After labeling them, inspection
of further sectors clarified that both sources are dippers (see plots
in Appendix~\ref{app:vetting}).  In addition, TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, but
nonetheless leave it in our catalog as an indication of possible
ambiguities in our search process.  TIC 57830249 (TWA~33) also has
previously detected 1.3\,mm continuum emission
\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
present.  It is also a dipper.
Given these ``errors'', plausible evolutionary connections between CQVs and
dippers are discussed in Section~\ref{subsec:discdippers}.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f5.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
      epoch over three years.  Each panel shows one (stacked) TESS
      orbit; small text denotes relative cycle number.  There are 200
      binned black points per cycle.  The TESS pointing law dictates
      time gaps; larger gaps tend to yield larger shape changes.  The
      dips usually evolve over tens to hundreds of cycles.  However
      cycles 1233-1264 show a dip that ``switched'' from a depth and
      duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
      cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}

\end{figure*}

@@

\subsection{Extremes}
The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
is the first time that it has been noted as a CQV.  The three
brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
TIC~167664935 ($T$=10.3).  The shortest period belongs to
TIC~201789285, at 3.64\,hr.  The longest period belongs to
TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).

@@

\subsection{Dust, or gas?}
We believe that the most likely scenarios to explain the overall CQV
phenomenology are the dust clump scenario, or the prominence scenario
(Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
centrifugally supported at the corotation radius.  The prominence idea
has a longer history, based first on analogy with quiescent
prominences/filaments observed to exist in the solar corona for up to
a few weeks \citep[see e.g.][]{2015ASSL..415.....V}.  In an extrasolar
context, spectroscopic detections of transient Balmer- and
resonance-line absorption seen for stars such as AB~Dor and Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
led to the interpretation that the data could best be explained by
similar prominence structures: cold, minimally ionized hydrogen clouds
or filaments that scatter chromospheric emission from the star to
produce the observed spectroscopic line variations
\citep[see][]{1989MNRAS.238..657C}.  The (short-term) mechanical
stability of such gas configurations has been demonstrated
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
interpretation of this class of observations seems at least somewhat
secure.

The link between the dense gas clumps (prominences) that likely exist
around rapidly rotating low-mass stars, and the CQV phenomenon, has
yet to be made.  A simple visual examination of the TESS light curves
for five prominence-hosting systems studied by
\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
V374 Peg--revealed no obvious CQV behavior, though all likely show
differential rotation, and Speedy~Mic shows two closely-spaced periods
and a strong beat.  Spectroscopically observable prominences therefore
do not imply CQV-like dips.

@@

Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
somewhat challenging to get neutral hydrogen to have this type of
chromaticity.  Bound-bound absorption provides opacity only at narrow
resonant lines.  Bound-free absorption can provide
wavelength-dependent opacity, but the absorption coefficients
generally {\it grow} with increasing wavelength, rather than {\it
shrink} as one needs in order to get deeper absorption in the blue
than in the red.  H$^-$  fails as a viable opacity source for the same
reason: its absorption coefficient peaks near 8500\,\AA, and is an
order of magnitude smaller at $\approx$3000\AA.
\citep{1992oasp.book.....G}, following \citet{1979MNRAS.187P..59W}.
Thompson scattering is also ruled out, because it is gray.  Dust, with
its relatively featureless but increasing extinction curve when going
bluer into the optical \citep{1989ApJ...345..245C}, is to our
knowledge the most obvious opacity source.

While the above line of reasoning seems fairly convincing, it has a
flaw.  The logic presented above would imply that regardless of a
star's temperature, if relative depths of a dip are seen to be deeper
in the blue than in the red, then it is hard to get hydrogen to do it.
There is however a rapidly rotating magnetic B-star, $\sigma$~Ori~E,
which shows dips that are deeper in the blue than in the red
\citep{1977ApJ...216L..31H}.  Photometric and spectroscopic
observations of this star have been understood in terms of absorbing
circumstellar material, quite analogous to the geometries we are
discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
material however cannot be dust, due to the relevant sublimation
timescales.  It is instead thought to be sourced from bound-free
absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
Separate and smaller amplitude emission in that system may also come
from electrons scattering photospheric light toward the observer when
the clouds are not in transit \citep{2022MNRAS.511.4815B}.

@@

@@

Ultimately, there are a few problems for the idea of a disintegrating
planetesimal.  First, a large number of the dips show asymmetries in
the {\it wrong direction} relative to the naive expectation of a
trailing comet tail.  Invoking non-exponentially decaying dust
distributions as a function of azimuth might be one way out of this,
but such an idea would need stronger theoretical footing.  More
important is that the (unseen) planets or planetesimals should be on
{\it exactly periodic} orbits over observable timescales, on the
presumption that the planetesimals would be massive enough to not feel
any headwind or magnetic field.  For most CQVs, this is inconsistent
with the data; dips in sources such as LP 12-502 appear and disappear
at {\it distinct phases}, but with the same period.  It seems
challenging to reconcile this behavior with the possible presence of
just a single launching body.  Finally, the fact that the dips often
respond to events like flares suggests that that the responsible
material be much less massive than a 1--100-\,km sized planetesimal,
and therefore more easily influenced by the stellar magnetic field.

@@

\begin{itemize}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample seem to remain fixed over the span of available
    observations, the light curve shapes themselves evolve, similar to
    rotating stars.
	%
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles.
	%
  \item The CQV phenomenon persists for at least 150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri.  It may extend to even older ages, however the lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    phenomenon does become less common at older ages.
	%
  \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
	%
  \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
\end{itemize}

Many questions remain.  Is the eclipsing material responsible for the
phenomenon gas, or dust?  After correcting for line-of-sight
inclination, do most M-dwarfs go through a phase of trapping material
a few stellar radii away from their surfaces?  What observational
signatures distinguish the proposed models (Figure~\ref{fig:f1},
bottom row)?  What organizational regularities characterize the CQV as
a class of variable star?  What physically sets the extremes of the
CQV population, such as the longest rotation periods, hottest stellar
temperatures, and oldest stellar ages?  And finally, what connections,
if any, do CQVs have to topics such as stellar evolution, M-dwarf
magnetic fields, debris disks, and close-in exoplanets?  While we have
tried to point out possible connections, the most likely path toward
definitive resolutions would be to observe a full phase curve of LP
12-502, or perhaps some other suitable object, using JWST/MIRI.

{\bf lgb: final paragraph(s) clearly need improvement!}

@@

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
GAB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission, and advised RJ on his contributions.
All authors assisted in manuscript revision.

@@

>>>>

\newcommand{\rprs}{{$R_p/R_{\star}$}}
\newcommand{\vsini}{{$V \sin i$}}
\newcommand{\kms}{{km\,s$^{-1}$}}
\newcommand{\gcc}{{g\,cm$^{-3}$}}
\newcommand{\rstar}{{$R_\star$}}
\newcommand{\rhostar}{{$\rho_\star$}}
\newcommand{\mearth}{{M$_\oplus$}}
\newcommand{\rearth}{{R$_\oplus$}}
\newcommand{\rsun}{{R$_\odot$}}
\newcommand{\msun}{{M$_\odot$}}
\newcommand{\bprp}{G_{\rm BP} - G_{\rm RP}}

@@

@@

All pre-main-sequence stars vary in optical brightness, and the origin
of such variability is, in most cases, understood.  Well-explored
sources of optical variability include inhomogeneities on stellar
surfaces such as starspots and faculae \citep{2021isma.book.....B},
occultations by gas-rich circumstellar disks
\citep{2017MNRAS.470..202B}, and, in geometrically favorable
circumstances, eclipses by stars and planets
\citep{2010exop.book...55W}.  More exotic forms of optical variability
relevant to this work include transiting exocomets (e.g.~$\beta$~Pic;
\citealt{2019A&A...625L..13Z}) and disintegrating rocky bodies around
both M-dwarfs (e.g. KOI-2700; \citealt{2014ApJ...784...40R}) and white
dwarfs (e.g. WD~1145; \citealt{2015Natur.526..546V}).

@@

A word on nomenclature.  CQVs have been called ``transient and
persistent flux dips'', ``scallop shells'', ``batwings'',
\citep{2017AJ....153..152S} ``complex rotators'',
\citep{2019ApJ...876..127Z,2022AJ....163..144G,2023ApJ...945..114P}
and ``complex periodic variables'' \citep{2023MNRAS.518.2921K}.  
The CQVs should generally not be conflated with ``dippers'', which are classical T
Tauri stars with infrared excesses, and drastically and 
at best marginally periodic variability linked
to obscuring inner disk structures and accretion hot spots
\citep{2014AJ....147...82C,2021ApJ...908...16R}.  
With that said, a few similarities between CQVs and dippers do exist
(see Sections~\ref{subsec:irexcess} and~\ref{subsec:discdippers}).
At the risk of
introducing yet another standard, we prefer a nomenclature that
reflects how, when observed over timescales of more than tens of
cycles, CQVs are almost but not exactly periodic.  They are
irregularly periodic, or for short, quasiperiodic.  While the
three-type classification scheme proposed by
\citet{2017AJ....153..152S} may indeed provide some helpful visual
distinctions amongst CQV sub-classes, it seems likely that they are
all explained by a single underlying phenomenon, and so we opt to
refer to them by a single empirically descriptive name.

@@

		\vspace{-0.6cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f1b.pdf}
		}
	\end{center}
		\vspace{-0.3cm}
	\caption{
		{\bf Complex quasiperiodic variables (CQVs)}:
		{\it Top:} Phase-folded TESS light curves of three CQVs.  Each is
		stacked over one month.  Gray are raw 2-minute data; black bins to
		300 points per cycle.  Periods in hours are in the bottom right of
		each panel.  Left-to-right, the objects are LP 12-502
		(TIC 402980664; Sector~19), TIC 94088626 (Sector 10), and TIC
		425933644 (Sector~28).
		{\it Bottom:} Cartoon models for the phenomenon.  The dust clump
		scenario
		(lower left) and prominence scenario (lower center) both invoke centrifugally-supported material at the
		corotation radius.
		We disfavor the screen scenario (see Section~\ref{sec:intro}).
	}
	\label{fig:f1}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.96\textwidth]{annotated_lp12502.pdf}
		\vspace{-0.3cm}
		\caption{
			{\bf Validation plots used to  label CQVs}.  The complete figure
			set, with one image per sector for each of \ncpvsfound\ CQVs
			and candidate CQVs
			is available online {\bf For internal collaboration review:
				\url{https://www.dropbox.com/scl/fo/zlj3txot4cvymfb22wewu/h?dl=0&rlkey=3ec5f9o5xewrixzfkhkdenopa}}.
			Panels are as follows.
			{\it a)}: Phase-folded light curve; gray points are raw 2-minute
			data and black points are binned to 200 points per cycle.
			{\it b)}: Phase-dispersion minimization (PDM) periodogram.
			Dotted lines show up to the 10$^{\rm th}$ harmonic and
			subharmonic.
			{\it c)}: DSS finder chart, with 1- and 2-TESS pixel radius
			circles displayed for scale.
			{\it d)}: Cleaned light curve, binned to 20-minute cadence, in
			Barycentric TESS Julian Date (BTJD).
			{\it e)}: Phase-folded light curve, binned to 100 points per
			cycle.  The gray line denotes the automated spline-fit to the
			wrapped phase-folded light curve, and small gray triangles
			denote automatically identified local minima.
			{\it f)}: Phase-folded light curve at twice the peak period.
			{\it g)}: Phase-folded light curve at half the peak period.
			{\it h)}: Phase-folded time-series within the ``background''
			aperture defined in the SPOC light curves.
			{\it i)}: Phase-folded flux-weighted centroid in the column
			direction.
			{\it j)}: Phase-folded flux-weighted centroid in the row
			direction.
			{\it k)}: Gaia DR2 color--absolute magnitude diagram.     
			The gray background denotes stars within 100\,pc.
			{\it l)}: Information from Gaia DR2, TIC8, and the automated
			dip-counting search pipeline.  ``Neighbors'', abbreviated
			``nbhr'', are listed within apparent distances of 2 TESS pixels
			if $\Delta T$$<$2.5.
			{\it m)}: BANYAN-$\Sigma$ v1.2 association probabilities, calculated
			using positions, proper motions, and the parallax.
		}
		\label{fig:vet}
	\end{center}
\end{figure*}

We visually assessed whether the objects found using the Fourier
(Section~\ref{subsec:fourier}) and dip-counting
(Section~\ref{subsec:counting}) techniques were consistent with
expectations for CQVs by assembling the data shown in
Figure~\ref{fig:vet}.  We labeled a star as a ``good'' CQV if
at least one TESS sector showed what we viewed as the unambiguous
signatures of the class (short period; at least three dips or else
otherwise oddly-shaped dips; relative stability over a timescale of
30\,days).  We also noted stars that we thought could be CQVs, but
that were more ambiguous with a ``maybe'' flag.

@@

The two ``good'' IR excesses belonged to ``candidate'' CQVs
TIC~193136669 (TWA~34) and TIC~57830249 (TWA~33).  Both are in the TW
Hydrae association ($\approx$10\,Myr), and have relatively long
periods of 38\,hr and 44\,hr respectively.  In our initial labeling,
we labeled both as ``maybe'' CQVs because the dips in their light
curves did not show the rigid periodicity typical of CQVs;  their
periods were also relatively long.  After labeling them, inspection
of further sectors clarified that both sources are dippers (see plots
in Figure~\ref{fig:vet}).  In addition, TIC 193136669 has a cold
molecular disk based on observed 1.3\,mm continuum emission and
resolved Keplerian $^{12}{\rm CO}(2-1)$ emission
\citep{2015A&A...582L...5R}.  It was also labeled a dipper by
\citet{2022ApJS..263...14C}; we agree with their designation, but
nonetheless leave it in our catalog as an indication of possible
ambiguities in our search process.  TIC 57830249 (TWA~33) also has
previously detected 1.3\,mm continuum emission
\citep{2015A&A...582L...5R}, suggestive of cold dust grains being
present.  It is also a dipper.
Given these ``errors'', plausible evolutionary connections between CQVs and
dippers are discussed in Section~\ref{subsec:discdippers}.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f5.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Evolution of LP 12-502} ($P$=18.6\,h) at fixed period and
      epoch over three years.  Each panel shows one (stacked) TESS
      orbit; small text denotes relative cycle number.  There are 200
      binned black points per cycle.  The TESS pointing law dictates
      time gaps; larger gaps tend to yield larger shape changes.  The
      dips usually evolve over tens to hundreds of cycles.  However
      cycles 1233-1264 show a dip that ``switched'' from a depth and
      duration of 3\% and 3\,hr to 0.3\% and 1\,hr over less than one
      cycle (cf.~Figure~\ref{fig:lplc}).
		}
		\label{fig:lp}
	\end{center}
\end{figure*}

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs from our serach}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The \nstarssearched\ target stars with 120-second cadence data
      acquired by TESS between July~2018 and Sep~2022 are shown as the shaded background on the top panels,
      where darker regions correspond to a larger relative number of observed stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

\subsection{Typical and Extreme Cases}
\label{subsec:extreme}
Figure~\ref{fig:catalogscatter} shows some of the derived properties
for our CQV catalog, and contrasts them against both the target star
sample (top panels), and the population of rotating stars in the Pleiades
from \citet{2016AJ....152..114R}.
Generally, CQVs are much younger than typical field stars. 
In terms of their rotation, relative to the Pleiades,
they are among the more rapidly rotating half.
The dearth of $T$$>$15.5 CQVs in our sample, despite our search extending
to $T$$=$16, is a consequence of the 120-second selection function.
%

The closest CQV in our catalog is DG~CVn (TIC~368129164;
$d$$=$18\,pc), a member of AB Dor.  To our knowledge, this manuscript
is the first time that it has been noted as a CQV.  The three
brightest CQVs are DG~CVn ($T$=9.3), TIC~405754448 ($T$=9.6), and
TIC~167664935 ($T$=10.3).  The shortest period belongs to
TIC~201789285, at 3.64\,hr.  The longest period belongs to
TIC~405910546, at 37.9\,hr.  If the latter source turns out to be an
eclipsing binary, the next-longest would be TIC~193831684 (31.0\,hr).

@@

\subsection{Dust, or gas?}
We believe that the most likely scenarios to explain CQVs
are either the dust clump scenario or the prominence scenario
(Figure~\ref{fig:f1}).  Both invoke clumpy material that would be
centrifugally supported at the corotation radius.  The prominence idea
has a longer history, based first on analogy with quiescent
prominences/filaments observed to exist in the solar corona for up to
a few weeks \citep[see e.g.][]{2015ASSL..415.....V}.  In an extrasolar
context, spectroscopic detections of transient Balmer- and
resonance-line absorption seen for stars such as AB~Dor and Speedy~Mic
\citep[e.g.][]{1989MNRAS.238..657C,1993MNRAS.262..369J,2006MNRAS.365..530D,2016MNRAS.463..965L}
led to the interpretation that the data could best be explained by
similar prominence structures: cold, minimally ionized hydrogen clouds
or filaments that scatter chromospheric emission from the star to
produce the observed spectroscopic line variations
\citep[see][]{1989MNRAS.238..657C}.  The (short-term) mechanical
stability of such gas configurations is theoretically plausible
\citep{2000MNRAS.316..647F,2022MNRAS.514.5465W}, and the
interpretation of this class of observations seems at least somewhat
secure.

Any link between the dense gas clumps (prominences) that likely exist
around rapidly rotating low-mass stars and the CQV phenomenon has
yet to be made.  A simple visual examination of the TESS light curves
for five prominence-hosting systems studied by
\citet{2019MNRAS.482.2853J}--AB~Dor, Speedy~Mic, LQ Lup, HK Aqr, and
V374 Peg--revealed no obvious CQV behavior, though all show
differential evolution, and Speedy~Mic shows two closely-spaced periods
and a strong beat.  Spectroscopically observable prominences 
do not imply CQV-like dips.

@@

Based on our reading of \citet[][Ch.~8]{1992oasp.book.....G}, it seems
somewhat challenging to get neutral hydrogen to have this type of
chromaticity.  Bound-bound absorption provides opacity only at narrow
resonant lines.  Bound-free absorption can provide
wavelength-dependent opacity, but the absorption coefficients
generally {\it grow} with increasing wavelength, rather than {\it
shrink} as one needs in order to get deeper absorption in the blue
than in the red.  H$^-$  fails as a viable opacity source for the same
reason: its absorption coefficient peaks near 8500\,\AA, and is an
order of magnitude smaller at $\approx$3000\AA.
(\citealt{1992oasp.book.....G}, following \citealt{1979MNRAS.187P..59W}).
Thompson scattering is also ruled out, because it is gray.  Dust, with
its relatively featureless but increasing extinction curve when going
bluer into the optical \citep{1989ApJ...345..245C}, is to our
knowledge the most obvious opacity source.

While the reasoning above seems fairly convincing, it has a
flaw.  The argument presented above would imply that regardless of a
star's temperature, if relative depths of a dip are seen to be deeper
in the blue than in the red, then it is hard to get hydrogen to do it.
There is however a rapidly rotating magnetic B-star, $\sigma$~Ori~E,
which shows dips that are deeper in the blue than in the red
\citep{1977ApJ...216L..31H}.  Photometric and spectroscopic
observations of this star have been understood in terms of absorbing
circumstellar material, quite analogous to the geometries we are
discussing for much cooler M-dwarfs \citep{2005ApJ...630L..81T}.  This
material however cannot be dust, due to the relevant sublimation
timescales.  It is instead thought to be sourced from bound-free
absorption from neutral hydrogen \citep{2005ApJ...630L..81T}.
Separate and smaller amplitude emission in that system may also come
from electrons scattering photospheric light toward the observer when
the clouds are not in transit \citep{2022MNRAS.511.4815B}.

@@

\subsubsection{The lifetime constraint}
Independent of the microphysical basis for gas absorption, the observed
lifetime of the CQV phenomenon could provide another dimension to discern between
the gas {\it vs.} dust clump scenarios.
Based on the available statistics from the studies of L.~Rebull and J.~Stauffer,
it seems plausible that CQV occurrence decreases in time, bottoming to zero
well before the $\approx$700\,Myr age of Praesepe.
This is odd in the context of the prominence scenario, because pre-main-sequence
M-dwarfs spin up over the first $\approx$$10^8$\,yr;
prominences might even be expected to be {\it more} common at the 
age of the Pleiades than for younger stars.
This broadly assumes that any star that can support prominences will,
which translates in detail to a condition on the star's mass, rotation
period, and magnetic field strength.
Based on the degree to which M-dwarfs remain rapid rotators over the first 700\,Myr
\citep[e.g. Figure~13 of][]{2022AJ....164...80R}, 
it seems surprising in the gas clump (prominence) scenario that no stars
older than 150\,Myr have been seen to exhibit the phenomenon.
In the dust clump scenario this is not a problem, because the dust could
be externally sourced, and would be expected to have a finite supply.

@@

Ultimately, there are a few problems for the idea of a disintegrating
planetesimal.  First, a large number of the dips show asymmetries in
the {\it wrong direction} relative to the naive expectation of a
trailing comet tail.  Invoking non-exponentially decaying dust
distributions as a function of azimuth might be one way out of this,
but such an idea would need stronger theoretical footing.  More
important is that the (unseen) planets or planetesimals should be on
{\it exactly periodic} orbits over observable timescales, on the
presumption that the planetesimals would be massive enough to not feel
any headwind or magnetic field.  For most CQVs, this is inconsistent
with the data; dips in sources such as LP 12-502 appear and disappear
at {\it distinct phases}, but with the same period.  It seems
challenging to reconcile this behavior with the possible presence of
just a single launching body.  Finally, the fact that the dips often
respond to events like flares suggests that that the responsible
material be much less massive than a 1--100\,km sized planetesimal,
and therefore more easily influenced by the stellar magnetic field.

@@

\begin{enumerate}
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample seem to remain fixed over the span of available
    observations, the light curve shapes themselves evolve, similar to
    rotating stars.
	%
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles.
  	%
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
    %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes.
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or a factor of 100
    larger if the material is gas.
    %
  \item The CQV phenomenon persists for at least 150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri.  It may extend to even older ages, however the lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon may be limited to the first few hundred
    million years.
	%
  \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
  \item Observed CQVs span a stellar mass range of 0.1-0.8\,M$_\odot$ (Section~\ref{subsec:extreme}).
\end{enumerate}

Many questions remain.  Is the eclipsing material responsible for the
phenomenon gas, or dust?  After correcting for line-of-sight
inclination, do most M-dwarfs go through a phase of trapping material
a few stellar radii away from their surfaces?  What observational
signatures distinguish the proposed models?
What physically sets the extremes of the
CQV population, such as the longest rotation periods, hottest stellar
temperatures, and oldest stellar ages?  And finally, what connections,
if any, do CQVs have to topics such as stellar evolution, M-dwarf
magnetic fields, debris disks, and close-in exoplanets?  
Additional theoretical work could help in resolving many of these questions,
and would contain rich puzzles in plasma physics, MHD, and radiative transfer, in
addition to the dynamos of young, fully-convective stars.

On the observational front, expanding our analysis of the TESS data to the full frame images
could yield a truly volume-limited selection function, and would
expand the CQV census within 50\,pc by about a factor of two.
Out to larger volume (e.g.~200\,pc), the yield boost would be more
than an order of magnitude.
While such studies would be important for improving our understanding
of CQV population demographics,
independent programs aimed at acquiring
mid- and high-resolution time-series spectroscopy hold the best chance
at detecting
either gas or dust absorption signatures over the span of any
given CQV cycle.
The challenges intrinsic to such observations seem worth the effort.

@@

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
GAB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission.
All authors assisted in manuscript revision.

@@

\clearpage
